Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-03 neurips-20/cvx-flats.tex

\begin{theorem}\label{thm:cvx-flats}
  Let a property $\gamma:\simplex\toto\R$ be given, let $p\in\simplex$ such that either (i) $|\gamma(p)|=1$ or (ii) $\gamma$ is elicitable and $p\in\relint\simplex$, and let $r\in\gamma(p)$.
Then if $L: \reals^d \times \Y \to \reals$ indirectly elicits $\gamma$, there is a flat $F$ with $p\in F \cap \simplex \subseteq \gamma_r$ and $\codim(F) \leq d$.
% COmmented 06.03.20
%	If there is a convex surrogate loss $L : \reals^d \times\Y \to \reals$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
\end{theorem}
\begin{proof}
	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$, so that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
	Fix $p \in \simplex$ and $r \in \gamma(p)$.
  \jessie{Show that there is some $u \in \Gamma(p)$ such that $\psi(u) = r$.}
	We will show $F \cap \simplex \subseteq \Gamma_u$; the result then follows from $\Gamma_u \subseteq \gamma_r$.
	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p} \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.
  % (Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.)

@@

While this work tightens bounds on the dimension of consistent surrogate losses, it does not completely characterize the dimensionality of a convex surrogate for a given problem.
One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
In discrete predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\citet{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
Lastly, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
\raft{Infinite $\Y$}

@@

Our bounds from Theorem~\ref{thm:cvx-flats} on the distribution $p = (1/5, 3/5, 1/5)$ suggest that the convex elicitation complexity $\eliccvx(\Gamma) \geq 3 - 0 -1 = 2$, since there is no way to draw a line through $p$ while staying in just one level set on the simplex.
This bound is the same as those given by feasible subspace dimension, but we cannot apply~\citet[Theorem 16]{ramaswamy2016convex}, which makes a statement about convex calibration dimension, since we do not have a target loss.

>>>>

\begin{theorem}\label{thm:cvx-flats}
  Let a property $\gamma:\simplex\toto\R$ be given, let $p\in\simplex$ such that either (i) $|\gamma(p)|=1$ or (ii) $\gamma$ is elicitable and $p\in\relint\simplex$, and let $r\in\gamma(p)$.
Then if $L: \reals^d \times \Y \to \reals$ indirectly elicits $\gamma$, there is a flat $F$ with $p\in F \cap \simplex \subseteq \gamma_r$ and $\codim(F) \leq d$.
% COmmented 06.03.20
%	If there is a convex surrogate loss $L : \reals^d \times\Y \to \reals$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
\end{theorem}
\begin{proof}
	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$, so that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
	We now claim there is some $u \in \Gamma(p)$ with $\psi(u) = r$.
	First, if $|\gamma(p)| = 1$, then any $u \in \Gamma(p)$ must link to $r$ as we contradict indirect elicitation otherwise; we would have $p \in \Gamma_u$ but $p \not \in \gamma_{\psi(u)}$.
	Now if $\gamma$ is elicitable and $p \in \relint{\simplex}$, we know that $\psi(u) = r'$ for some $r' \in \R$.%suppose there is another $r' \in \R$ with $r \neq r'$ and $r' \in \gamma(p)$.
	If $r' \neq r$, we can show $p \in F \cap \simplex \subseteq \gamma_{r'} (\iff p \in F \cap \simplex \subseteq \gamma_{r})$, where the if and only if comes from Lemma~\ref{lem:set-valued-prop-flats}.
%	Fix $p \in \simplex$ and $r \in \gamma(p)$.
  \jessie{Show that there is some $u \in \Gamma(p)$ such that $\psi(u) = r$.}
	We will show $F \cap \simplex \subseteq \Gamma_u$; the result then follows from $\Gamma_u \subseteq \gamma_r$.
	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p} \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.
  % (Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.)

@@

While this work tightens bounds on the dimension of consistent surrogate losses, it does not completely characterize the dimensionality of a convex surrogate for a given problem.
One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
In discrete predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\citet{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
Moreover, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
Lastly, Theorem~\ref{thm:cvx-flats} relies on Minkowski sums, which have not been clearly defined for infinite $\Y$; we leave this generalization as an open question.

@@

Since $\Gamma$ is not elicitable, we cannot apply Theorem~\ref{thm:cvx-flats} for the distribution $p = (3/4, 1/8,1/8)$, since $\Gamma(p) = \{$rainy, snowy, sunny$\}$.
However, our bounds from Theorem~\ref{thm:cvx-flats} on the distribution $q = (1/10, 7/10, 1/5)$, which we can apply since $\Gamma(q) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\Gamma) \geq 3 - 0 -1 = 2$, since there is no way to draw a line through $q$ while staying in just one level set on the simplex.

\citet[Theorem 16]{ramaswamy2016convex} cannot draw any conclusions about this property for two reasons that go hand in hand: first, we are given a target property instead of a target loss.
Second, since the property is not elicitable (hence why there can be no target loss), we observe $\dim(\Sc_{\Gamma_{\text{rainy}}}(p)) \neq \dim(\Sc_{\Gamma_{\text{sunny}}}(p))$, so their result cannot be applied as~\citet[Lemma 23]{ramaswamy2016convex} does not hold.
